A Makefile for Developing Containerized \LaTeX\ Technical Documents

### 2021-09-21 ms.tex
init

tmp/$(results): $(results_code)
	build image $(results_image)
	run container $(results_image) $(VERSION)

@@

The Makefile can be called with the following options:
\begin{lstlisting}[language=bash, style=lststyle, caption={Makefile options.}]
make                # Generate draft (fast) version.\ 
make VERSION=--full # Generate full (slow) version.\ 
make clean          # Remove tmp/ directory.
\end{lstlisting}

The \textit{author} may use the Makefile for developing \textit{documents} in the following way:
\begin{enumerate}
	\item clones/downloads the repository which consists of the Makefile and the set of files as depicted in Fig.\ref{fig:repositoryfiles},
	\item creates and develops the \textit{results code}.
	\item creates and develops the \textit{\LaTeX\ code}.
	\item executes \textit{make} for fast development iterations and experimentation,
	\item executes \textit{make VERSION=-{}-full} for distribution or publication and
	\item executes \textit{make clean} to restore to a clean state.
\end{enumerate}

>>>>

tmp/$(results): $(results_code)
	build image $(results_image)
	run container $(results_image)

@@

The Makefile can be called with the following options:
\begin{lstlisting}[language=bash, style=lststyle, caption={Makefile options.}]
make                # Generate draft (fast) version.\ 
make FULL=1         # Generate full (slow) version.\ 
make clean          # Remove tmp/ directory.
\end{lstlisting}

The \textit{author} may use the Makefile for developing \textit{documents} in the following way:
\begin{enumerate}
	\item clones/downloads the repository which consists of the Makefile and the set of files as depicted in Fig.\ref{fig:repositoryfiles},
	\item creates and develops the \textit{results code}.
	\item creates and develops the \textit{\LaTeX\ code}.
	\item executes \textit{make} for fast development iterations and experimentation,
	\item executes \textit{make FULL=1} for distribution or publication and
	\item executes \textit{make clean} to restore to a clean state.
\end{enumerate}
